Non-English Conditional Entropy and Mutual Information

### 2019-05-30 entropy/Wikipedia/wiki_clustering.Rmd
reorganized surprisal folder more

models %>%
  mutate(coeffs = map(model, tidy)) %>%
  select(-data, -model) %>%
  unnest() %>%
  filter(term == "cosine") %>%
  arrange(desc(statistic)) %>%
  write_feather(here("word_order_glm_absolute.feather"))
```

>>>>

models %>%
  mutate(coeffs = map(model, tidy)) %>%
  select(-data, -model) %>%
  unnest() %>%
  filter(term == "cosine") %>%
  arrange(desc(statistic)) 
```

### 2019-05-30 extensions/CogSci 2019 paper/position-info.tex
reorganized surprisal folder more

\begin{abstract}
Although languages vary widely in their structure, all are vehicles for
the transmission of information. Consequently, aspects of speakers' word
choice can be understood through models of optimal communication. One
prediction of these models is that speakers should keep the density of
information constant over the duration of an utterance (R. P. Levy \&
Jaeger, 2007). However, different languages have different structural
properties that constrain the space of a speaker's choices
(e.g.~canonical word order). We build on a method developed by Yu, Cong,
Liang, \& Liu (2016) to analyze the word-level entropy curves of natural
language productions across a diverse set of languages and in diverse
written and spoken contexts. We show that languages impose
characteristic constraints on speaker's choices that predict deviations
from Uniform Information Density, and that cross-linguistic variability
in these deviations is predictable in part from syntactic properties of
those languages.

@@

Over 7,000 languages are spoken around the modern world (Simons \&
Fenning, 2018). These languages vary along many dimensions, but all
share a core goal: communicating information. If speakers and writers of
these languages act near-optimally to achieve their communicative goals,
regularities of use across these diverse languages can be explained by a
rational theory of communication (Anderson, 1991). Information theory, a
mathematical framework developed by Shannon (1948) to describe the
transmission and decoding of signals, has been a unifying approach for
the recent development of theories of communication in human and machine
language processing (Jelinek, 1976; R. P. Levy \& Jaeger, 2007).

These theories model the process of communication as transmission of
information over a noisy channel. The producer begins with an intended
meaning, packages this meaning into language, and then sends the encoded
meaning to their intended receiver over a communicative channel. The
receiver must then decode the producer's intended meaning from the
signal they receive on their end of the channel. The problem is that
this channel is noisy, and sometimes the signal can be corrupted
(e.g.~the producer can misspeak, or the receiver can mishear). In order
to maximize the probability that the correct meaning is transmitted,
these theories predict that producers should choose linguistic messages
that keep the rate of information constant across words. The intuition
is that if the receiver misperceives a word, and that word contains most
of the information in the sentence, then the communication will have
failed. Because producers cannot predict which word a speaker will
mishear, their best strategy is spread the information evenly across all
of the words in a sentence, i.e.~maintain \emph{Uniform Information
Density} (Genzel \& Charniak, 2002; R. P. Levy \& Jaeger, 2007).

The evidence in favor of Uniform Information Density has largely focused
on specific points within sentences, while the hypothesis itself has
been applied broadly over the past decade. The original evidence in
favor of Uniform Information Density in R. P. Levy \& Jaeger (2007)
finds that the insertion of complementizers (e.g. ``that'') in relative
clauses in English corresponds to where neighboring words have high
information content. Similarly, A. F. Frank \& Jaeger (2008) argues that
contractions in English such as ``you're'' do not occur when neighboring
words are highly informative. Applications of Uniform Information
Density include determining whether linguistic alignment takes place
(Jaeger \& Snider, 2013), Zipfian word length distributions (Piantadosi,
Tily, \& Gibson, 2011), communication efficiency (Mahowald, Fedorenko,
Piantadosi, \& Gibson, 2013), dialogue and turn-taking (Xu \& Reitter,
2018) and the significance of ambiguity in language (Piantadosi, Tily,
\& Gibson, 2012), among other research.

However, other recent work has contradicted the Uniform Information
Density hypothesis. Similar to the original work in R. P. Levy \& Jaeger
(2007), Zhan \& Levy (2018) focuses on information distribution at
particular points in sentences. Zhan \& Levy (2018) finds that more
information-rich classifiers in Mandarin Chinese are produced when
production of the neighboring noun is difficult, not when the
information content is high. Examining the information density at the
sentence level, Jain, Singh, Ranjan, Rajkumar, \& Agarwal (2018) study
word order across written sentences in Hindi, a freer word order
language than English, and find that information density has no
significant effect on determining a Hindi writer's word order.

@@

\subsection{Calculating entropy
curves}\label{calculating-entropy-curves}

@@

With this measure, we can compute the unigram positional entropy at each
word position of sentences of each length within a corpus. The result of
this method across word positions can be plotted for each sentence
length as an \emph{entropy curve}, which can be visually compared across
sentence lengths to observe how the unigram entropy changes across
absolute positions in each of the sentences. Genzel \& Charniak (2002)
similarly examine a unigram entropy measure on sentences, and found that
entropy at the sentence level increases linearly with sentence index
within a corpus. Uniform Information Density applies this uniformity of
entropy rate in sentences to all levels of speech (R. P. Levy \& Jaeger,
2007), and so our method obtained from Yu et al. (2016), which examines
text at the word level, should find a monotonically increasing affine
function at the word level.

@@

\section{Study 1}\label{study-1}

@@

\subsection{Data and Analysis}\label{data-and-analysis}

@@

\subsection{Results}\label{results}

@@

\section{Study 2}\label{study-2}

@@

\subsection{Data and Analysis}\label{data-and-analysis-1}

@@

\subsection{Results}\label{results-1}

@@

\section{Study 3}\label{study-3}

@@

\subsection{Data and Analysis}\label{data-and-analysis-2}

@@

\subsection{Results}\label{results-2}

@@

\section{General Discussion}\label{general-discussion}

@@

\section{References}\label{references}

\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent

\hypertarget{refs}{}
\hypertarget{ref-anderson1991}{}
Anderson, J. R. (1991). The adaptive nature of human categorization.
\emph{Psychological Review}, \emph{98}(3), 409.

\hypertarget{ref-aylett2004}{}
Aylett, M., \& Turk, A. (2004). The smooth signal redundancy hypothesis:
A functional explanation for relationships between redundancy, prosodic
prominence, and duration in spontaneous speech. \emph{Language and
Speech}, \emph{47}(1), 31--56.

\hypertarget{ref-bai2008}{}
Bai, X., Yan, G., Liversedge, S. P., Zang, C., \& Rayner, K. (2008).
Reading spaced and unspaced chinese text: Evidence from eye movements.
\emph{Journal of Experimental Psychology: Human Perception and
Performance}, \emph{34}(5), 1277.

\hypertarget{ref-clear1993}{}
Clear, J. H. (1993). The british national corpus. \emph{The Digital
World}, 163--187.

\hypertarget{ref-demuth2006}{}
Demuth, K., Culbertson, J., \& Alter, J. (2006). Word-minimality,
epenthesis and coda licensing in the early acquisition of english.
\emph{Language and Speech}, \emph{49}(2), 137--173.

\hypertarget{ref-dryer2013}{}
Dryer, M. S., \& Haspelmath, M. (2013). \emph{The world atlas of
language structures online}. Max Planck Institute for Evolutionary
Anthropology.

\hypertarget{ref-ferrer-i-cancho2013}{}
Ferrer-i-Cancho, R., Debowski, L., \& Prado Martin, F. M. del. (2013).
Constant conditional entropy and related hypotheses. \emph{Journal of
Statistical Mechanics: Theory and Experiment}, \emph{2013}(07), L07001.

\hypertarget{ref-frank2008}{}
Frank, A. F., \& Jaeger, T. F. (2008). Speaking rationally: Uniform
information density as an optimal strategy for language production. In
\emph{Proceedings of the annual meeting of the cognitive science
society} (Vol. 30).

\hypertarget{ref-genzel2002}{}
Genzel, D., \& Charniak, E. (2002). Entropy rate constancy in text. In
\emph{Proceedings of the 40th annual meeting on association for
computational linguistics} (pp. 199--206). Association for Computational
Linguistics.

\hypertarget{ref-godfrey1992}{}
Godfrey, J. J., Holliman, E. C., \& McDaniel, J. (1992). SWITCHBOARD:
Telephone speech corpus for research and development. In
\emph{Acoustics, speech, and signal processing, 1992. icassp-92., 1992
ieee international conference on} (Vol. 1, pp. 517--520). IEEE.

\hypertarget{ref-jaeger2013}{}
Jaeger, T. F., \& Snider, N. E. (2013). Alignment as a consequence of
expectation adaptation: Syntactic priming is affected by the prime's
prediction error given both prior and recent experience.
\emph{Cognition}, \emph{127}(1), 57--83.

\hypertarget{ref-jain2018}{}
Jain, A., Singh, V., Ranjan, S., Rajkumar, R., \& Agarwal, S. (2018).
Uniform information density effects on syntactic choice in hindi. In
\emph{Proceedings of the workshop on linguistic complexity and natural
language processing} (pp. 38--48).

\hypertarget{ref-jelinek1976}{}
Jelinek, F. (1976). Continuous speech recognition by statistical
methods. \emph{Proceedings of the IEEE}, \emph{64}(4), 532--556.

\hypertarget{ref-kuperman2010}{}
Kuperman, V., Dambacher, M., Nuthmann, A., \& Kliegl, R. (2010). The
effect of word position on eye-movements in sentence and paragraph
reading. \emph{The Quarterly Journal of Experimental Psychology},
\emph{63}(9), 1838--1857.

\hypertarget{ref-landauer1997}{}
Landauer, T. K., \& Dumais, S. T. (1997). A solution to plato's problem:
The latent semantic analysis theory of acquisition, induction, and
representation of knowledge. \emph{Psychological Review}, \emph{104}(2),
211.

\hypertarget{ref-levy2007}{}
Levy, R. P., \& Jaeger, T. F. (2007). Speakers optimize information
density through syntactic reduction. In \emph{Advances in neural
information processing systems} (pp. 849--856).

\hypertarget{ref-li2015}{}
Li, H., \& Zhou, J. (2015). \emph{Study on dinner table talk of
preschool children family in shanghai} (Master's thesis). East China
Normal University.

\hypertarget{ref-macwhinney2014}{}
MacWhinney, B. (2014). \emph{The childes project: Tools for analyzing
talk, volume ii: The database}. Psychology Press.

\hypertarget{ref-mahowald2013}{}
Mahowald, K., Fedorenko, E., Piantadosi, S. T., \& Gibson, E. (2013).
Info/information theory: Speakers choose shorter words in predictive
contexts. \emph{Cognition}, \emph{126}(2), 313--318.

\hypertarget{ref-piantadosi2011}{}
Piantadosi, S. T., Tily, H., \& Gibson, E. (2011). Word lengths are
optimized for efficient communication. \emph{Proceedings of the National
Academy of Sciences}, \emph{108}(9), 3526--3529.

\hypertarget{ref-piantadosi2012}{}
Piantadosi, S. T., Tily, H., \& Gibson, E. (2012). The communicative
function of ambiguity in language. \emph{Cognition}, \emph{122}(3),
280--291.

\hypertarget{ref-sanchez2019}{}
Sanchez, A., Meylan, S. C., Braginsky, M., MacDonald, K. E., Yurovsky,
D., \& Frank, M. (in press). Childes-db: A flexible and reproducible
interface to the child language data exchange system. \emph{Behavior
Research Methods}. in press.

\hypertarget{ref-shannon1948}{}
Shannon, C. E. (1948). A mathematical theory of communication.
\emph{Bell System Technical Journal}, \emph{27}(3), 379--423.

\hypertarget{ref-shiro2000}{}
Shiro, M. (2000). Diferencias sociales en la construcción del`` yo'' y
del`` otro'': Expresiones evaluativas en la narrativa de niños
caraqueños en edad escolar. In \emph{Lengua, discurso, texto: I simposio
internacional de análisis del discurso} (pp. 1303--1318). Visor.

\hypertarget{ref-simons2018}{}
Simons, G. F., \& Fenning, C. D. (Eds.). (2018). \emph{Ethnologue:
Languages of the world, 21st edition}. Dallas, Texas: SIL International.

\hypertarget{ref-stivers2009universals}{}
Stivers, T., Enfield, N. J., Brown, P., Englert, C., Hayashi, M.,
Heinemann, T., \ldots{} others. (2009). Universals and cultural
variation in turn-taking in conversation. \emph{Proceedings of the
National Academy of Sciences}, pnas--0903616106.

\hypertarget{ref-stowe2018}{}
Stowe, L. A., Kaan, E., Sabourin, L., \& Taylor, R. C. (2018). The
sentence wrap-up dogma. \emph{Cognition}, \emph{176}, 232--247.

\hypertarget{ref-xu2018}{}
Xu, Y., \& Reitter, D. (2018). Information density converges in
dialogue: Towards an information-theoretic model. \emph{Cognition},
\emph{170}, 147--163.

\hypertarget{ref-yu2016}{}
Yu, S., Cong, J., Liang, J., \& Liu, H. (2016). The distribution of
information content in english sentences. \emph{arXiv Preprint
arXiv:1609.07681}.

\hypertarget{ref-zhan2018}{}
Zhan, M., \& Levy, R. (2018). Comparing theories of speaker choice using
a model of classifier production in mandarin chinese. In
\emph{Proceedings of the 2018 conference of the north american chapter
of the association for computational linguistics: Human language
technologies, volume 1 (long papers)} (Vol. 1, pp. 1997--2005).

>>>>

\begin{abstract}
Although languages vary widely in their structure, all are vehicles for
the transmission of information. Consequently, aspects of speakers' word
choice can be understood through models of optimal communication. One
prediction of these models is that speakers should keep the density of
information constant over the duration of an utterance (Levy \& Jaeger,
2007). However, different languages have different structural properties
that constrain the space of a speaker's choices (e.g.~canonical word
order). We build on a method developed by Yu, Cong, Liang, \& Liu (2016)
to analyze the word-level entropy curves of natural language productions
across a diverse set of languages and in diverse written and spoken
contexts. We show that languages impose characteristic constraints on
speaker's choices that predict deviations from Uniform Information
Density, and that cross-linguistic variability in these deviations is
predictable in part from syntactic properties of those languages.

@@

Over 7,000 languages are spoken around the modern world (Simons \&
Fenning, 2018). These languages vary along many dimensions, but all
share a core goal: communicating information. If speakers and writers of
these languages act near-optimally to achieve their communicative goals,
regularities of use across these diverse languages can be explained by a
rational theory of communication (Anderson, 1991). Information theory, a
mathematical framework developed by Shannon (1948) to describe the
transmission and decoding of signals, has been a unifying approach for
the recent development of theories of communication in human and machine
language processing (Jelinek, 1976; Levy \& Jaeger, 2007).

These theories model the process of communication as transmission of
information over a noisy channel. The producer begins with an intended
meaning, packages this meaning into language, and then sends the encoded
meaning to their intended receiver over a communicative channel. The
receiver must then decode the producer's intended meaning from the
signal they receive on their end of the channel. The problem is that
this channel is noisy, and sometimes the signal can be corrupted
(e.g.~the producer can misspeak, or the receiver can mishear). In order
to maximize the probability that the correct meaning is transmitted,
these theories predict that producers should choose linguistic messages
that keep the rate of information constant across words. The intuition
is that if the receiver misperceives a word, and that word contains most
of the information in the sentence, then the communication will have
failed. Because producers cannot predict which word a speaker will
mishear, their best strategy is spread the information evenly across all
of the words in a sentence, i.e.~maintain \emph{Uniform Information
Density} (Genzel \& Charniak, 2002; Levy \& Jaeger, 2007).

The evidence in favor of Uniform Information Density has largely focused
on specific points within sentences, while the hypothesis itself has
been applied broadly over the past decade. The original evidence in
favor of Uniform Information Density in Levy \& Jaeger (2007) finds that
the insertion of complementizers (e.g. ``that'') in relative clauses in
English corresponds to where neighboring words have high information
content. Similarly, Frank \& Jaeger (2008) argues that contractions in
English such as ``you're'' do not occur when neighboring words are
highly informative. Applications of Uniform Information Density include
determining whether linguistic alignment takes place (Jaeger \& Snider,
2013), Zipfian word length distributions (Piantadosi, Tily, \& Gibson,
2011), communication efficiency (Mahowald, Fedorenko, Piantadosi, \&
Gibson, 2013), dialogue and turn-taking (Xu \& Reitter, 2018) and the
significance of ambiguity in language (Piantadosi, Tily, \& Gibson,
2012), among other research.

However, other recent work has contradicted the Uniform Information
Density hypothesis. Similar to the original work in Levy \& Jaeger
(2007), Zhan \& Levy (2018) focuses on information distribution at
particular points in sentences. Zhan \& Levy (2018) finds that more
information-rich classifiers in Mandarin Chinese are produced when
production of the neighboring noun is difficult, not when the
information content is high. Examining the information density at the
sentence level, Jain, Singh, Ranjan, Rajkumar, \& Agarwal (2018) study
word order across written sentences in Hindi, a freer word order
language than English, and find that information density has no
significant effect on determining a Hindi writer's word order.

@@

\hypertarget{calculating-entropy-curves}{%
\subsection{Calculating entropy
curves}\label{calculating-entropy-curves}}

@@

With this measure, we can compute the unigram positional entropy at each
word position of sentences of each length within a corpus. The result of
this method across word positions can be plotted for each sentence
length as an \emph{entropy curve}, which can be visually compared across
sentence lengths to observe how the unigram entropy changes across
absolute positions in each of the sentences. Genzel \& Charniak (2002)
similarly examine a unigram entropy measure on sentences, and found that
entropy at the sentence level increases linearly with sentence index
within a corpus. Uniform Information Density applies this uniformity of
entropy rate in sentences to all levels of speech (Levy \& Jaeger,
2007), and so our method obtained from Yu et al. (2016), which examines
text at the word level, should find a monotonically increasing affine
function at the word level.

@@

\hypertarget{study-1}{%
\section{Study 1}\label{study-1}}

@@

\hypertarget{data-and-analysis}{%
\subsection{Data and Analysis}\label{data-and-analysis}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

\hypertarget{study-2}{%
\section{Study 2}\label{study-2}}

@@

\hypertarget{data-and-analysis-1}{%
\subsection{Data and Analysis}\label{data-and-analysis-1}}

@@

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

@@

\hypertarget{study-3}{%
\section{Study 3}\label{study-3}}

@@

\hypertarget{data-and-analysis-2}{%
\subsection{Data and Analysis}\label{data-and-analysis-2}}

@@

\hypertarget{results-2}{%
\subsection{Results}\label{results-2}}

@@

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}

\noindent

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-anderson1991}{}%
Anderson, J. R. (1991). The adaptive nature of human categorization.
\emph{Psychological Review}, \emph{98}(3), 409.

\leavevmode\hypertarget{ref-aylett2004}{}%
Aylett, M., \& Turk, A. (2004). The smooth signal redundancy hypothesis:
A functional explanation for relationships between redundancy, prosodic
prominence, and duration in spontaneous speech. \emph{Language and
Speech}, \emph{47}(1), 31--56.

\leavevmode\hypertarget{ref-bai2008}{}%
Bai, X., Yan, G., Liversedge, S. P., Zang, C., \& Rayner, K. (2008).
Reading spaced and unspaced chinese text: Evidence from eye movements.
\emph{Journal of Experimental Psychology: Human Perception and
Performance}, \emph{34}(5), 1277.

\leavevmode\hypertarget{ref-clear1993}{}%
Clear, J. H. (1993). The british national corpus. \emph{The Digital
World}, 163--187.

\leavevmode\hypertarget{ref-demuth2006}{}%
Demuth, K., Culbertson, J., \& Alter, J. (2006). Word-minimality,
epenthesis and coda licensing in the early acquisition of english.
\emph{Language and Speech}, \emph{49}(2), 137--173.

\leavevmode\hypertarget{ref-dryer2013}{}%
Dryer, M. S., \& Haspelmath, M. (2013). \emph{The world atlas of
language structures online}. Max Planck Institute for Evolutionary
Anthropology.

\leavevmode\hypertarget{ref-ferrer-i-cancho2013}{}%
Ferrer-i-Cancho, R., Debowski, L., \& Prado Martin, F. M. del. (2013).
Constant conditional entropy and related hypotheses. \emph{Journal of
Statistical Mechanics: Theory and Experiment}, \emph{2013}(07), L07001.

\leavevmode\hypertarget{ref-frank2008}{}%
Frank, A. F., \& Jaeger, T. F. (2008). Speaking rationally: Uniform
information density as an optimal strategy for language production. In
\emph{Proceedings of the annual meeting of the cognitive science
society} (Vol. 30).

\leavevmode\hypertarget{ref-genzel2002}{}%
Genzel, D., \& Charniak, E. (2002). Entropy rate constancy in text. In
\emph{Proceedings of the 40th annual meeting on association for
computational linguistics} (pp. 199--206). Association for Computational
Linguistics.

\leavevmode\hypertarget{ref-godfrey1992}{}%
Godfrey, J. J., Holliman, E. C., \& McDaniel, J. (1992). SWITCHBOARD:
Telephone speech corpus for research and development. In
\emph{Acoustics, speech, and signal processing, 1992. ICASSP-92., 1992
ieee international conference on} (Vol. 1, pp. 517--520). IEEE.

\leavevmode\hypertarget{ref-jaeger2013}{}%
Jaeger, T. F., \& Snider, N. E. (2013). Alignment as a consequence of
expectation adaptation: Syntactic priming is affected by the prime's
prediction error given both prior and recent experience.
\emph{Cognition}, \emph{127}(1), 57--83.

\leavevmode\hypertarget{ref-jain2018}{}%
Jain, A., Singh, V., Ranjan, S., Rajkumar, R., \& Agarwal, S. (2018).
Uniform information density effects on syntactic choice in hindi. In
\emph{Proceedings of the workshop on linguistic complexity and natural
language processing} (pp. 38--48).

\leavevmode\hypertarget{ref-jelinek1976}{}%
Jelinek, F. (1976). Continuous speech recognition by statistical
methods. \emph{Proceedings of the IEEE}, \emph{64}(4), 532--556.

\leavevmode\hypertarget{ref-kuperman2010}{}%
Kuperman, V., Dambacher, M., Nuthmann, A., \& Kliegl, R. (2010). The
effect of word position on eye-movements in sentence and paragraph
reading. \emph{The Quarterly Journal of Experimental Psychology},
\emph{63}(9), 1838--1857.

\leavevmode\hypertarget{ref-landauer1997}{}%
Landauer, T. K., \& Dumais, S. T. (1997). A solution to plato's problem:
The latent semantic analysis theory of acquisition, induction, and
representation of knowledge. \emph{Psychological Review}, \emph{104}(2),
211.

\leavevmode\hypertarget{ref-levy2007}{}%
Levy, R. P., \& Jaeger, T. F. (2007). Speakers optimize information
density through syntactic reduction. In \emph{Advances in neural
information processing systems} (pp. 849--856).

\leavevmode\hypertarget{ref-li2015}{}%
Li, H., \& Zhou, J. (2015). \emph{Study on dinner table talk of
preschool children family in shanghai} (Master's thesis). East China
Normal University.

\leavevmode\hypertarget{ref-macwhinney2014}{}%
MacWhinney, B. (2014). \emph{The childes project: Tools for analyzing
talk, volume ii: The database}. Psychology Press.

\leavevmode\hypertarget{ref-mahowald2013}{}%
Mahowald, K., Fedorenko, E., Piantadosi, S. T., \& Gibson, E. (2013).
Info/information theory: Speakers choose shorter words in predictive
contexts. \emph{Cognition}, \emph{126}(2), 313--318.

\leavevmode\hypertarget{ref-piantadosi2011}{}%
Piantadosi, S. T., Tily, H., \& Gibson, E. (2011). Word lengths are
optimized for efficient communication. \emph{Proceedings of the National
Academy of Sciences}, \emph{108}(9), 3526--3529.

\leavevmode\hypertarget{ref-piantadosi2012}{}%
Piantadosi, S. T., Tily, H., \& Gibson, E. (2012). The communicative
function of ambiguity in language. \emph{Cognition}, \emph{122}(3),
280--291.

\leavevmode\hypertarget{ref-sanchez2019}{}%
Sanchez, A., Meylan, S. C., Braginsky, M., MacDonald, K. E., Yurovsky,
D., \& Frank, M. (in press). Childes-db: A flexible and reproducible
interface to the child language data exchange system. \emph{Behavior
Research Methods}.

\leavevmode\hypertarget{ref-shannon1948}{}%
Shannon, C. E. (1948). A mathematical theory of communication.
\emph{Bell System Technical Journal}, \emph{27}(3), 379--423.

\leavevmode\hypertarget{ref-shiro2000}{}%
Shiro, M. (2000). Diferencias sociales en la construcción del" yo" y
del" otro": Expresiones evaluativas en la narrativa de niños caraqueños
en edad escolar. In \emph{Lengua, discurso, texto: I simposio
internacional de análisis del discurso} (pp. 1303--1318). Visor.

\leavevmode\hypertarget{ref-simons2018}{}%
Simons, G. F., \& Fenning, C. D. (Eds.). (2018). \emph{Ethnologue:
Languages of the world, 21st edition}. Dallas, Texas: SIL International.

\leavevmode\hypertarget{ref-stivers2009universals}{}%
Stivers, T., Enfield, N. J., Brown, P., Englert, C., Hayashi, M.,
Heinemann, T., \ldots{} others. (2009). Universals and cultural
variation in turn-taking in conversation. \emph{Proceedings of the
National Academy of Sciences}, pnas--0903616106.

\leavevmode\hypertarget{ref-stowe2018}{}%
Stowe, L. A., Kaan, E., Sabourin, L., \& Taylor, R. C. (2018). The
sentence wrap-up dogma. \emph{Cognition}, \emph{176}, 232--247.

\leavevmode\hypertarget{ref-xu2018}{}%
Xu, Y., \& Reitter, D. (2018). Information density converges in
dialogue: Towards an information-theoretic model. \emph{Cognition},
\emph{170}, 147--163.

\leavevmode\hypertarget{ref-yu2016}{}%
Yu, S., Cong, J., Liang, J., \& Liu, H. (2016). The distribution of
information content in english sentences. \emph{arXiv Preprint
arXiv:1609.07681}.

\leavevmode\hypertarget{ref-zhan2018}{}%
Zhan, M., \& Levy, R. (2018). Comparing theories of speaker choice using
a model of classifier production in mandarin chinese. In
\emph{Proceedings of the 2018 conference of the north american chapter
of the association for computational linguistics: Human language
technologies, volume 1 (long papers)} (Vol. 1, pp. 1997--2005).

### 2019-05-30 extensions/Language Dev. Proj./LDP_entropy.Rmd
reorganized surprisal folder more

```{r filter_utterances}
get_ses_utterances <- function(status, utterances, home_visits) {
  income <- home_visits %>% filter(income_category %in% status)

  ids <- unique(income$id) %>% unlist()

  utterances %>% filter(subject %in% ids)
}

ses_utts <- get_ses_utterances(c(6), utterances, home_visits)
```

```{r ldp_analysis}
get_unigram_entropies <- function(role, sen_length, utterances) {

  if(role == "child") {
    sub_utterances <- utterances %>%
      filter(c_utts_orig != "") %>%
      mutate(length = str_count(c_utts_orig, " |\\+|_") + 1)

      colnames(sub_utterances)[colnames(sub_utterances)=="c_utts_orig"] <- "gloss"
  } else {
     sub_utterances <- utterances %>%
      filter(p_utts_orig != "") %>%
      mutate(length = str_count(p_utts_orig, " |\\+|_") + 1)

      colnames(sub_utterances)[colnames(sub_utterances)=="p_utts_orig"] <- "gloss"
  }

@@

  tokens %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = sen_length)
}

entropies <- map(2:10, ~get_unigram_entropies("child", .x, ses_utts)) %>%
  bind_rows()

ggplot(entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)
```

>>>>

```{r filter_utterances}
get_ses_utterances <- function(status, utterances, home_visits) {
  ids <- home_visits %>% 
    filter(income_category %in% status)  %$% 
    id %>% 
    unique() %>% 
    unlist()

  utterances %>% filter(subject %in% ids)
}
```

```{r entropy}
get_unigram_entropies <- function(role, sen_length, utterances) {

  if(role == "child") {
    sub_utterances <- utterances %>%
      filter(c_utts_orig != "") %>%
      mutate(length = str_count(c_utts_orig, " |\\+|_") + 1)
      colnames(sub_utterances)[colnames(sub_utterances)=="c_utts_orig"] <- "gloss"
  } else {
     sub_utterances <- utterances %>%
      filter(p_utts_orig != "") %>%
      mutate(length = str_count(p_utts_orig, " |\\+|_") + 1) 
      colnames(sub_utterances)[colnames(sub_utterances)=="p_utts_orig"] <- "gloss"
  }

@@

  tokens %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = sen_length)
}
```

```{r ldp_analysis}
STATUS <- c(1)

ses_utts <- get_ses_utterances(STATUS, utterances, home_visits)

entropies_child <- map(2:10, ~get_unigram_entropies("child", .x, ses_utts)) %>%
  bind_rows()

ggplot(entropies_child, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)

entropies_adult <- map(2:10, ~get_unigram_entropies("not child", .x, ses_utts)) %>%
  bind_rows()

ggplot(entropies_adult, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)

entropies_all <- bind_rows(entropies_adult, entropies_child)

ggplot(entropies_all, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper, color = role)) +
  facet_wrap(~ length) + 
  geom_pointrange(position = position_dodge(.25)) +
  geom_smooth(se = F) +
  ggtitle("Child and Adult Entropy Distributions (LDP SES Bracket 1)")
```
